### 2021-08-01 README.Rmd
Adjusting readme

-   [:file_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
-   [:file_folder: data](/analysis/data): Data used in the analysis.
-   [:file_folder: figures](/analysis/figures): Plots and other
    illustrations
-   [:file_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents prepared
    and collected during the analysis.

>>>>

-   [:file_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
-   [:file_folder: data](/analysis/data): Data used in the analysis.
-   [:file_folder: figures](/analysis/figures): Plots and other
    illustrations
